---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spaceobs

<!-- badges: start -->
<!-- badges: end -->

The goal of spaceobs is to provide an analysis of the data set of yearly number of objects launched into outer space through shiny app build inside this package.

Tou can access the package website through this [link](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-suppawish11/)

## Installation

You can install the development version of spaceobs like so:

``` r
# install.packages("remotes")
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-suppawish11")
```

## Example

```{r example}
library(spaceobs)
```

#### Dataset
```{r eval=FALSE}
space_objects
```

To view the yearly number of objects launched into outer space dataset.

#### Entity list
```{r}
entity_list() |> 
  head()
```

To retrieve the entity names that are in the `space_objects` dataset.

#### Year range of selected entity
```{r}
year_entity("United States")
```

To retrieve the year range of the selected entity in the `space_objects` dataset.

#### Launching Shiny App

```{r eval=FALSE}
run_app()
```

