---
title: "Space Objects Launched"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Space Objects Launched}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The dataset used in this package is from [Our World in Data](https://ourworldindata.org/grapher/yearly-number-of-objects-launched-into-outer-space?facet=none#explore-the-data).

This vignette is providing the information on the dataset and functions in this spaceobs package.

### Use package

Using `library()` to load `spaceobs` package.
```{r setup}
library(spaceobs)
```

### Dataset

Data description of `space_objects` dataset
```{r eval=FALSE}
space_objects
```

| **Variable** | **Description**                                    |
|--------------|----------------------------------------------------|
| Entity       | Entity, country or other entity                    |
| Code         | Entity code, country or other entity code          |
| Year         | Year                                               |
| num_objects  | Annual number of objects launched into outer space |

### Entity list
Using `entity_list()` function to get the list of the entity that is in the `space_objects` dataset.
```{r eval=FALSE}
entity_list() 
```

### Year range of entity
Using `year_entity()` function and specify the entity name from the `entity_list()` function to get the range of year of the selected entity.

```{r}
year_entity("United States")
```

### Shiny App
In this package there is build in shiny app that include the analysis from of the `space_objects` dataset from `run_app()` function.

**Purpose of Shiny App**

As space exploration continues to expand, it is essential to track and analyze the growing number of objects launched into orbit or beyond.

The purpose of this analysis is to:  

  - Highlight the entity that launched the highest number of objects into the outer space.  
  - Explore the space technological advancement from the number of objects launched into the outer space.  
  - Raise awareness of the overall trends in space exploration.  
  
The app use an interactive plots to allow users to observe the information of their interest year and entity that are in the data.

```{r eval=FALSE}
run_app()
```






